Fluent statistical computing interfaces for biological data analysis

### 2020-07-09 Rmd/04-intron.Rmd
rejig chapter 4
rejigging sections for chapter

# Tidy coverage analysis and visualisation with superintronic {#ch:intron}

@@

@@

## Data

@@

## Results

### Discovery of regions of interest via 'ranglers'

### A superintronic workflow for uncovering intron retention

>>>>

# Exploratory coverage analysis with superintronic and plyranges {#ch:intron}

@@

### Discovery of regions of interest via 'data descriptors'

## A workflow for uncovering intron retention

@@

@@
